\documentclass[class=article, crop=false]{standalone}
\usepackage[subpreambles=true]{standalone}
\usepackage{import}
\usepackage{amsmath}
\usepackage{enumitem} % Format list spacing 

\begin{document}
\subsection{Implementations}
The following is an incomplete list of implementations of Root.

\subsubsection{0x77700005BEA4DE0A78b956517f099260C2CA9a26}
The Root contract address is 0x77700005BEA4DE0A78b956517f099260C2CA9a26 \newline(\term{i.e.}, \Root\ = 0x77700005BEA4DE0A78b956517f099260C2CA9a26).

\paragraph{Current Parameters}
The following are the current parameters of 0x77700005BEA4DE0A78b956517f099260C2CA9a26:
\begin{itemize}[itemsep=3pt,leftmargin=16pt]
    \item The owner of 0x77700005BEA4DE0A78b956517f099260C2CA9a26 is \newline0xb7774ec5031e1d903152E96BbC1601e5D0D83Ca2 (\term{i.e.}, the \term{Root DAO Multisig});
    \item The address of Beanstalk is 0xC1E088fC1323b20BCBee9bd1B9fC9546db5624C5; and
    \item $\Root^{\text{min}}$ = 0.1\%.
\end{itemize}

\paragraph{Minting Whitelist}
The following ERC-20 Standard tokens are on the Beanstalk \term{Deposit} \term{Whitelist} and \term{Whitelisted} for \term{Minting} \Root:

\begin{itemize}[itemsep=3pt,leftmargin=16pt]
    \item 0xBEA0000029AD1c77D3d5D23Ba2D8893dB9d1Efab (\term{i.e.}, \Bean).
\end{itemize}

\paragraph{Governance}
A robust decentralized governance mechanism must balance the principles of decentralization with resistance to attempted protocol changes, both malicious and ignorant, and the ability to quickly adapt to changing information. 

0x77700005BEA4DE0A78b956517f099260C2CA9a26 is governed by Root DAO. Root DAO governs upgrades to 0x77700005BEA4DE0A78b956517f099260C2CA9a26, the use of \term{Stalk} in Beanstalk governance and the treatment of non-Beanstalk-native yield earned by \newline0x77700005BEA4DE0A78b956517f099260C2CA9a26. Any account that owns \Root\ can participate in Root DAO governance.

\subparagraph{RIPs}

Any account that owns more than $\Root^{\text{RIP}}$, such that $\Root^{\text{RIP}} \in \{j \times 10^{-18} \mid j \in \mathbb{N},\ j \leq 10^{18} \}$, of total outstanding \Root\ can submit a \term{RIP} to the Root DAO Snapshot\fref{snapshot.org/\#/rootsmoney.eth} via the \term{Root DAO Multisig}.

Root DAO only accepts votes in favor of \term{RIPs}. An account's vote for a given \term{RIP} is counted as the minimum of its \Root\ between the beginning and end of the \term{Voting Period}. 

A \term{Voting Period} begins when a vote for a \term{RIP} can be submitted to Snapshot and ends at approximately the beginning of the 169th Beanstalk \term{Season} after it begins, or when the \term{RIP} is committed with a supermajority.

If at the end of the \term{Voting Period}:
\begin{itemize}[midsep]
    \item Less than or equal to half of the total outstanding eligible \Root\ votes in favor of the \term{RIP}, it fails; and
    \item More than half of the total outstanding eligible \Root\ votes in favor of the \term{RIP}, it passes.
\end{itemize}

If at any time before the end of the \term{Voting Period} more than two-thirds of the total outstanding eligible \Root\ votes in favor of the \term{RIP}, it passes and can be committed to the Ethereum blockchain.

\subparagraph{Stalk Use}
In its capacity as a \term{Stalkholder}, 0x77700005BEA4DE0A78b956517f099260C2CA9a26 is entitled to vote on (1) each \term{Beanstalk Improvement Proposal} (\term{BIP}) and (2) other, non-\term{BIP}, governance processes, and may be entitled to non-Beanstalk-native yields.

Any \Root\ owner can submit a \term{Root Stalk Proposal} (\term{RSP}) to the \term{RSP} Snapshot\fref{snapshot.org/\#/rootstalkproposals.eth} to determine how Root should use its \term{Stalk} in each governance process, and distribute yields, if ever. \term{RSPs} follow the same structure as \term{RIPs}, except that the length of the \term{Voting Period} can be reasonably shortened to ensure the will of Root DAO can be reflected in the governance process.

Any \term{Beanstalk Improvement Proposal} (\term{BIP}) will automatically qualify to be proposed to Root DAO as an \term{RSP}.

The \term{Root DAO Multisig} will participate on each governance process as determined by the \term{RSP}.

\subparagraph{Root DAO Multisig}
The \term{Root DAO Multisig} is a 4-of-7 Safe\fref{app.safe.global/eth:0xb7774ec5031e1d903152E96BbC1601e5D0D83Ca2} multisig wallet with anonymous signers consisting of community members and contributors to Root and Beanstalk. The \term{Root DAO Multisig} will execute the will of Root DAO. The \term{Root DAO Multisig} will provide sufficient notice of the submission of a \term{RIP}, its contents and the beginning of its \term{Voting Period} before submitting a \term{RIP} to Snapshot, and will repost \term{BIPs} on the \term{RSP} Snapshot as soon as possible after they are posted to the Beanstalk DAO Snapshot.\fref{snapshot.org/\#/beanstalkdao.eth} In the future, we expect \term{RIPs} will implement permissionless governance and revoke these abilities from the \term{Root DAO Multisig}.

Thus, Root creates a robust decentralized governance mechanism.
\end{document}